---
title: "Relationship between learnability, expressivity and systematicity"
output: pdf_document
---

```{r echo=F, eval=F}
setwd("~/Documents/MPI/Thom/LEX_2016/analysis/")
```

# Introduciton

How does learnability correlate with:

-  Expressivity (number of unique labels)
-  Systematicity (correlation between lexical and semantic distances)
-  Mean word length of language
-  Distinctiveness (average levenshtein distance between word pairs)

# Load libraies

```{r warning=F, message=F}
library(dplyr)
library(party)
```

# Load data

```{r}
d = read.csv("../data/ExperimentData_with_all_Learnability.csv", stringsAsFactors = F)
```

```{r}

d.mean = d %>% group_by(phase,condition,loadFile) %>% 
  summarise(
  Learnability = mean(Learnability,na.rm=T),
  Expressivity = mean(Expressivity),
  Systematicity = mean(Systematicity),
  mean.word.length = mean(mean.word.length),
  distinctiveness = mean(distinctiveness)
)
d.mean = d.mean[!is.na(d.mean$Learnability),]
```

# Analysis

Look at the correlations between measures:

```{r}
cor.short = function(X,Y,la,lb){
  plot(X,Y,xlab=la,ylab=lb)
  cx= cor.test(X,Y)
  return(c(cor=cx$estimate, p=cx$p.value))
}

cor.short(d.mean$Learnability,d.mean$Expressivity,
          "Learnability","Expressivity")

cor.short(d.mean$Learnability,d.mean$Systematicity,
          "Learnability","Systematicity")

cor.short(d.mean$Learnability,d.mean$mean.word.length,
          "Learnability","Mean word length")

cor.short(d.mean$Learnability,d.mean$distinctiveness,
           "Learnability","Distinctiveness")
```

\newpage

# Decision tree

```{r}
ct = ctree(Learnability~Expressivity+Systematicity + distinctiveness + mean.word.length, data=d.mean)
plot(ct)
```

No partitions, suggesting there are no patterns in the data.